Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
Ditch incomplete discussion of attacks

Before an election is held, the election authority must construct four Tables that lie at the core
of the Scantegrity system: Tables P, Q, R, and S.

@@

\subsection{Clever attacks on verifiable voting systems}

Scantegrity \emph{II} claims to solve some issues with other/previous systems:
\begin{itemize}
	\item
		\term{Pattern voting} and
	\item
		\term{Randomization attacks}, whereby it's possible to tell whether a ballot is actually random
		or is ``biased.''
\end{itemize}

\todo{How much should we discuss here? What I said is very incomplete, but the Scantegrity II paper
doesn't say much more on the subject (instead deferring to other readings).}

>>>>

Before an election is held, the election authority must construct four Tables that lie at the core
of the Scantegrity system: Tables P, Q, R, and S (see ~\ref{fig:scantegrity}).

@@
